Detecting Facial Expressions in Professional Tennis Matches

### 2017-07-28 Report06-12.Rmd
AnimetricsFigure

  }
  if(matchBox){
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=FaceKey, group=FaceID), fill=NA) +
      guides(colour = "none")
  }
  else{
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=type, group=FaceID), fill=NA) +
      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
      coord_fixed(ratio=0.85)
    }

@@

# Results

@@

@@

\newpage
The image below is an example of how some faces were only found by certain APIs, and how some APIs produced unusual false discoveries.

@@

\newpage
We then considered the characteristics of the images that the API found Potential Faces in.

@@

mylist<-as.list(CompShot$file)
#6,7,8,
View(CompShot)
lapply(mylist[1:5], overlayGgplot)
overlayGgplot(mylist)
#decide on a comparison, one where images had faces both recognised manually, only one recognised by a software
```

@@

>>>>

  }
  if(matchBox){
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=FaceKey, group=FaceID), fill=NA) +
      guides(colour = "none")
  }
  else{
    group.colors <- c(Animetrics = "#B3E2CD",
                      Google = "#FDCDAC",
                      Manual = "#CBD5E8",
                      Microsoft = "#F4CAE4",
                      Skybiometry = "#E6F5C9")

    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=type, group=FaceID), fill=NA) +
      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
      coord_fixed(ratio=0.85) + scale_colour_manual(values=group.colors)
    }

@@

\newpage
# Results

## Amount of Potential Faces

@@

## Potential Faces Matching Manual Annotations

@@

## False Discoveries
The image below is an example of how some faces were only found by certain APIs, and how some APIs produced unusual false discoveries.

@@

## Image Characteristics

We then considered the characteristics of the images that the API found Potential Faces in.

@@

#mylist<-as.list(CompShot$file)
#6,7,8,
#View(CompShot)
#lapply(mylist[1:5], overlayGgplot)
#overlayGgplot(mylist)
#decide on a comparison, one where images had faces both recognised manually, only one recognised by a software
```

@@

```{r animetricsWeird, fig.cap=" Animetrics provided results that were quite unusual \\label{fig:animetricsWeird}" }
i1 <- "2016_CT6_R01_CGarcia_FRA_vs_BStrycova_CZE_WS145_clip.0015.png" %>% overlayGgplot()
i2 <- "2016_CT6_R01_EKulichkova_RUS_vs_APetkovic_GER_WS128_clip.0080.png" %>% overlayGgplot()
i3 <- "2016_CT6_R02_ABeck_GER_vs_TBacsinszky_SUI_WS220_clip.0017.png" %>% overlayGgplot()
grid.arrange(i1, i2, i3, nrow=2)
